### 2021-01-21 paper/localpsf.tex
edits
add changes based on meeting today

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		Compute spatially varying mean, $\mu$, and covariance, $\Sigma$, using Algorithm \ref{alg:varhpi_mean_cov}.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		Form constant function $C(x)=1$

@@

		\For{$i=1,2,\dots,d$}{
			Form linear function $L^i(x) = x^i$

			$\mu^i = \left(\mathcal{A}^T L^i\right)^* / \alpha$
		}
		\For{$i=1,2,\dots,d$}{
			\For{$j=1,\dots,i$}{
				Form quadratic function $Q^{ij} = x^i x^j$

@@

	}
	\caption{Compute volume $\alpha$, mean $\mu$, and covariance $\Sigma$}
	\label{alg:varhpi_mean_cov}
\end{algorithm2e}

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwProg{Fn}{Function}{}{}

	Start with a finite set of candidate points $P \subset \Omega$

	Initialize new empty batch of sample points, $S_b$

@@

		\If{$E_p \cap E_q \neq \{\}$ for all $q \in S_b$ and $E_p \cap \partial \Omega = \{\}$}{

@@

			Remove all points $x$ satisfying $\mu(x) \in E_p$ from $P$
		}
	}

@@

The \emph{Dirac comb}, $\xi_b$, associated with a batch of sample points $S_b$ is the sum of Dirac distributions (point sources) centered at the points $x_i \in S_b$. That is,
\begin{equation*}
	\xi^b := \sum_{x_i \in S_b} \delta_{x_i}.
\end{equation*}
For each batch $S_b$, we compute as the action of $\mathcal{A}$ on the associated Dirac comb:
\begin{equation}
\label{eq:dirac_comb_H_action}
	\eta^b := \langle\mathcal{A}, \xi^b\rangle^*.
\end{equation}
By linearity, $\eta^b$ may be written as
\begin{equation}
\label{eq:phi_b}
	\eta^b = \left\langle\mathcal{A},\sum_{x_i \in S_b} \delta_{x_i}\right\rangle^* = \sum_{x_i \in S_b} \langle\mathcal{A}, \delta_{x_i}\rangle^* = \sum_{x_i \in S_b} \phi_x.
\end{equation}
Since the points $x_i$ are chosen so that the support of $\phi_i$ and the support of $\phi_j$ do not overlap (or do not overlap much), we have
\begin{equation}
\label{eq:varphi_eval}
	\varphi_{x_i}(z) = \phi_i(z+x_i) = \begin{cases}
		\eta^b(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}.
		\end{cases}
\end{equation}
for all $x_i \in S_b$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover $\varphi_{x_i}$ for every point $x_i \in S_b$. To minimize memory usage, the functions $\varphi_i$ are never isolated and stored individually. Instead, we store the functions $\eta^b$, and use formula \eqref{eq:varphi_eval} to perform function evaluations $z \mapsto \varphi_i(z)$ as needed.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:psi_eq}
			\Delta \psi_i = \delta_{x_i} - C/|\Omega|, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$. Recall $\delta_{x_i}$ is a point source (delta distribution) centered at $x_i$, $C$ is the constant function $C(x)=1$, and $|\Omega|$ is the Lebesgue measure of $\Omega$.

			Compute $\theta_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:theta_eq}
			\Delta \theta_i = \psi_i, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

@@

		\For{$i=1,2,\dots,r$}{
			Compute
			\begin{equation}
			\label{eq:definition_of_alpha_alg}
			\alpha = \frac{\mathbf{1}^T S^{-1} e_i}{\mathbf{1}^T S^{-1} \mathbf{1}},
			\end{equation}
			where $\mathbf{1} = (1,1,\dots,1)$ is the length $r$ vector which has all components equal to one, and $e_i = (0,\dots,0,1,0,\dots,0)$ is the length $r$ vector with $i^\text{th}$ component equal to one and all other components equal to zero.

@@

\begin{algorithm2e}
	\SetAlgoNoLine

@@

	\Output{Boolean which is true if $E_p \cap E_q \neq \{\}$ and false otherwise}

	\mbox{}\\

	\Fn{$\ellipsoidsintersect{E_p}{E_q}$}
	{
		Solve generalized eigenvalue problem $\Sigma_p \Phi = \Sigma_q \Phi \Lambda$

@@

			\Return{False}

@@

			\Return{True}

		}
	}
	\caption{Determining whether two ellipsoids intersect}
	\label{alg:ellipsoid_intersection_test}
\end{algorithm2e}

>>>>

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\Input{Operator $\mathcal{A}$, parameter $\text{max\_batches}$}
		\Output{Dirac comb responses $\{\eta^b\}_{b=1}^{\text{max\_batches}}$, \\
			weighting functions $\{w_i\}_{i=1}^r$}

		Compute spatially varying mean, $\mu$, and covariance, $\Sigma$, using Algorithm \ref{alg:varhpi_mean_cov}.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\Input{Operator $\mathcal{A}$}
		\Output{$\alpha$, $\mu$, and $\Sigma$}

		\tcp{Compute scaling factor $\alpha$}

		Form constant function $C(x)=1$

@@

		\tcp{Compute mean $\mu$}
		\For{$i=1,2,\dots,d$}{
			Form linear function $L^i(x) = x^i$

			$\mu^i = \left(\mathcal{A}^T L^i\right)^* / \alpha$
		}
		\tcp{Compute covariance $\Sigma$}
		\For{$i=1,2,\dots,d$}{
			\For{$j=1,\dots,i$}{
				Form quadratic function $Q^{ij} = x^i x^j$

@@

	}
	\caption{Compute scaling factor $\alpha$, mean $\mu$, and covariance $\Sigma$}
	\label{alg:varhpi_mean_cov}
\end{algorithm2e}

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	\SetKwProg{Fn}{Function}{}{}

	\Input{Finite set of candidate points $P\subset \Omega$, \\mean $\mu(x)$ and covariance $\Sigma(x)$, \\domain boundary information $\partial \Omega$, \\previous sample point batches $S_1, \dots, S_{b-1}$}
	\Output{Batch of new sample points $S_b$}

	Initialize empty new batch of sample points, $S_b = \{\}$

@@

		\If{$E_p \cap E_q \neq \{\}$ for all $q \in S_b$ and $E_p \cap \partial \Omega = \{\}$}{
			\tcp{$E_p$ and $E_q$ are the ellipsoids defined in \eqref{eq:support_ellipsoid}}

@@

			Remove all points $p'$ satisfying $\mu(p') \in E_p$ from $P$
		}
	}

@@

The \emph{Dirac comb}, $\xi_b$, associated with a batch of sample points $S_b$ is the sum of Dirac distributions (point sources) centered at the points $x_i \in S_b$. That is,
\begin{equation*}
	\xi^b := \sum_{x_i \in S_b} \delta_{x_i}.
\end{equation*}
For each batch $S_b$, we compute as the action of $\mathcal{A}$ on the associated Dirac comb:
\begin{equation}
\label{eq:dirac_comb_H_action}
	\eta^b := \langle\mathcal{A}, \xi^b\rangle^*.
\end{equation}
By linearity, $\eta^b$ may be written as
\begin{equation}
\label{eq:phi_b}
	\eta^b = \left\langle\mathcal{A},\sum_{x_i \in S_b} \delta_{x_i}\right\rangle^* = \sum_{x_i \in S_b} \langle\mathcal{A}, \delta_{x_i}\rangle^* = \sum_{x_i \in S_b} \phi_x.
\end{equation}
Since the points $x_i$ are chosen so that the support of $\phi_i$ and the support of $\phi_j$ do not overlap (or do not overlap much), we have
\begin{equation}
\label{eq:varphi_eval}
	\varphi_{x_i}(z) = \phi_i(z+x_i) = \begin{cases}
		\eta^b(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}.
		\end{cases}
\end{equation}
for all $x_i \in S_b$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover $\varphi_{x_i}$ for every point $x_i \in S_b$. To minimize memory usage, the functions $\varphi_i$ are not stored individually. Instead, we store the functions $\eta^b$, and use formula \eqref{eq:varphi_eval} to perform function evaluations $z \mapsto \varphi_i(z)$ as needed.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\Input{Sample points $\{x_i\}_{i=1}^r$, domain geometry $\Omega$}
		\Output{Weighting functions $\{w_i\}_{i=1}^r$}

		Initialize constant function $C(x) = 1$

		Compute Lebesgue measure of the domain, $|\Omega|$

		\tcp{Compute harmonic functions $\{\psi_i\}_{i=1}^r$ and $\{\theta_i\}_{i=1}^r$}

		\For{$i=1,2, \dots, r$}{
			Initialize $\delta_{x_i}$ as the point source (delta distribution) centered at $x_i$.

			Compute $\psi_i$ by solving the Neumann Poisson problem
			\begin{equation}
			\label{eq:psi_eq}
			\begin{cases}
			\Delta \psi_i = \delta_{x_i} - C/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \psi_i = 0 & \text{on } \partial \Omega,
			\end{cases}
			\end{equation}
			with condition $\int_\Omega \psi_i(x) dx = 0$, where $\nu$ is the normal vector to $\partial \Omega$.

			Compute $\theta_i$ by solving the Neumann Poisson problem
			\begin{equation}
			\label{eq:theta_eq}
						\begin{cases}
			\Delta \theta_i = \psi_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \theta_i = 0 & \text{on } \partial \Omega,
			\end{cases}
			\end{equation}
			with condition $\int_\Omega \theta_i(x) dx = 0$, where $\nu$ is the normal vector to $\partial \Omega$.

@@

		\tcp{Compute weighting functions $\{w_i\}_{i=1}^r$}

		\For{$i=1,2,\dots,r$}{
			Compute
			\begin{equation}
			\label{eq:definition_of_alpha_alg}
			\alpha = \frac{\mathbf{1}^T S^{-1} e_i}{\mathbf{1}^T S^{-1} \mathbf{1}},
			\end{equation}
			where $\mathbf{1} = (1,1,\dots,1) \in \mathbb{R}^r$, and $e_i = (0,\dots,0,1,0,\dots,0)\in \mathbb{R}^r$ is unit vector with $i^\text{th}$ component equal to one.

@@

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}

	\Input{points $x \in \Omega$, $y \in \Omega$, \\sample point batches $S_1, \dots, S_\text{max\_batches}$, \\Dirac comb responses $\{\eta^b\}_{b=1}^{\text{max\_batches}}$, \\weighting functions $\{w_i\}_{i=1}^r$}
	\Output{Kernel entry $z = \widetilde{A}(y,x)$}

@@

	\Output{Boolean $\text{ellipsoids\_intersect}$ which is true if $E_p \cap E_q \neq \{\}$ and false otherwise}

	Solve generalized eigenvalue problem $\Sigma_p \Phi = \Sigma_q \Phi \Lambda$

@@

		$\text{ellipsoids\_intersect} \gets \text{False}$

@@

		$\text{ellipsoids\_intersect} \gets \text{True}$

	}
	\caption{Determining whether two ellipsoids intersect}
	\label{alg:ellipsoid_intersection_test}
\end{algorithm2e}
